### 2023-12-13 documentation/thesis/thesis_abstract.tex
thesis

Especially in the construction of low-field MRI devices based on
permanent magnets, a large number of magnets are used. In order to
realize a homogeneous B0 field with these magnets, which is necessary
for many setups, the magnetic properties of these magnets should be as
similar as possible.

Due to the complex manufacturing process, especially of neodymium
magnets, the different properties, especially the direction of
magnetization, can deviate from each other, which affects the
homogeneity of the field.

To adjust the field afterwards, a passive shimming process is typically
performed, which is complex and time-consuming and requires manual
corrections to the magnets used.

To avoid this process, magnets can be systematically measured in
advance. However, in this methodology, the recording, data storage and
subsequent evaluation of the data play an important role.

The various existing solutions implement individual aspects, but do not
provide a data pipeline from aqusation to analysis.

For this use case, the MagneticReadoutProcessing library was created,
which implements different aspects of data acquisition, data storage,
analysis, and each intermediate step can be customized by the user
without having to create everything from scratch, favoring an exchange
between different user groups.

>>>>

In the construction of low-field MRI devices based on permanent magnets,
a large number of magnets are used. In order to realize a homogeneous B0
field with these magnets, which is necessary for many setups, the
magnetic properties of these magnets have to be as similar to a certain
degree. Due to the complex manufacturing process of neodymium magnets,
the different properties, the direction of magnetization, can deviate
from each other, which affects the homogeneity of the field. To adjust
the field afterwards, a passive shimming process is typically performed,
which is complex and time-consuming and requires manual corrections to
the magnets used. To avoid this process, magnets can be systematically
measured in advance. In this methodology, the recording, data storage
and subsequent evaluation of the data play an important role. Various
existing open-source solutions implement individual parts, but do not
provide a complete data processing pipeline from aqusation to analysis
and the data storage formats of these are not compatible to each other.
For this use case, the MagneticReadoutProcessing library was created,
which implements all major aspects of acquisition, storage, analysis,
and each intermediate step can be customized by the user without having
to create everything from scratch, favoring an exchange between
different user groups. Complete documentation, tutorials and tests
enable users to use and adapt the FRamework as quickly as possible. The
framework for the characterisation of different N45 neodymium magnets,
which requires the integration of magnetic field sensors, was used for
the evaluation.

### 2023-12-13 documentation/thesis/thesis_document.tex
thesis

\hypertarget{fundamentals}{%
\chapter{Fundamentals}\label{fundamentals}}

\hypertarget{permanent-magnet-mri}{%
\section{Permanent magnet MRI}\label{permanent-magnet-mri}}

\hypertarget{typical-b0-magnet-structures}{%
\subsection{Typical B0 Magnet
structures}\label{typical-b0-magnet-structures}}

\hypertarget{shimming-procedure}{%
\section{Shimming procedure}\label{shimming-procedure}}

@@

\hypertarget{unified-sensor-interface}{%
\section{Unified Sensor Interface}\label{unified-sensor-interface}}

@@

\hypertarget{mechanical}{%
\section{Mechanical}\label{mechanical}}

@@

\hypertarget{software-implementation}{%
\chapter{Software implementation}\label{software-implementation}}

\hypertarget{library}{%
\section{Library}\label{library}}

@@

@@

\hypertarget{datastructures}{%
\subsection{Datastructures}\label{datastructures}}

\hypertarget{datapoints}{%
\subsubsection{Datapoints}\label{datapoints}}

\hypertarget{meta-data-management}{%
\subsubsection{Meta-Data management}\label{meta-data-management}}

\hypertarget{implementation}{%
\subsection{Implementation}\label{implementation}}

@@

\hypertarget{concepts-1}{%
\subsection{Concepts}\label{concepts-1}}

@@

@@

@@

\hypertarget{third-party-software-support}{%
\section{Third party software
support}\label{third-party-software-support}}

@@

@@

\hypertarget{distribution}{%
\subsection{Distribution}\label{distribution}}

\hypertarget{continuous-integration}{%
\subsection{Continuous Integration}\label{continuous-integration}}

\hypertarget{end-to-end-testing}{%
\subsection{End to end testing}\label{end-to-end-testing}}

@@

@@

>>>>

\hypertarget{background-and-motivation}{%
\section{Background and Motivation}\label{background-and-motivation}}

\hypertarget{low-field-mri}{%
\subsection{Low-Field MRI}\label{low-field-mri}}

\hypertarget{shimming-procedure}{%
\subsection{Shimming procedure}\label{shimming-procedure}}

\hypertarget{aim-of-this-thesis}{%
\section{Aim of this Thesis}\label{aim-of-this-thesis}}

\hypertarget{structure}{%
\section{Structure}\label{structure}}

@@

\hypertarget{conceptual-design}{%
\section{Conceptual design}\label{conceptual-design}}

\begin{itemize}
\tightlist
\item
  etnwicklung eines hardware uns software framework zur einfachen
  aquirierung von Meagnetfelddaten
\item
  analysetools und funktionen
\end{itemize}

\hypertarget{unified-sensor}{%
\chapter{Unified Sensor}\label{unified-sensor}}

\begin{itemize}
\tightlist
\item
  ziel ist es einen low cost hallsensor-interface zu entwickeln welcher
  möglichst
\item
  universell
\item
  verschienee sensoren abbilden kann
\item
  mit verschienden magneten typen und formen nutzbar
\item
  reproduzierbar
\item
  1d, 2d, 3d
\item
  integration
\end{itemize}

@@

\begin{itemize}
\item
  list of typical low cost hall sensors
\item
  =\textgreater{} alle i2c in der regel
\item ~
  \hypertarget{mechanical-structure}{%
  \section{Mechanical Structure}\label{mechanical-structure}}
\item
  3d druck toleranztest
\item
  magnet halterung mit kraftloser arretierung
\item
  motoren und andere unter umstaänden magnetische teile in der nähe des
  sensors
\item
  nylon schrauben, 3d druck, 3d gedruckte klemmverbindungen
\item
  später rausrechnen durch kalibierung
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  usb, ethernet
\item
  pps input output
\item
  multiplexer for i2c sensors alredy implemented
\end{itemize}

\hypertarget{firmware}{%
\section{Firmware}\label{firmware}}

\begin{itemize}
\tightlist
\item
  automatic sensor detation
\item
  serial cli support for manual mode
\item
  sync impulse =\textgreater{} 1 mastersensor als taktqelle
\item
  interene mittelung und speichern der werte im buffer
\item
  was durch den user implementiert werden muss klasse
\end{itemize}

\hypertarget{cli-interface}{%
\subsection{CLI Interface}\label{cli-interface}}

\begin{itemize}
\tightlist
\item
  einfache bedienung durch nutzer auch ohne weitere software
\item
  configuration
\item
  debugging
\end{itemize}

\hypertarget{example-sensors}{%
\section{Example Sensors}\label{example-sensors}}

\emph{anbei werden drei erschienee sensoren für unterschiedliche
anwedungfälle } tablle statisch dynamisch

\hypertarget{d-single-sensor}{%
\subsection{1D: Single Sensor}\label{d-single-sensor}}

\begin{figure}
\centering
\includegraphics{./generated_images/border_fullsphere_sensor.png}
\caption{fullsphere sensor \label{fullsphere_sensor.png}}
\end{figure}

\begin{itemize}
\tightlist
\item
  einfachster aufbau rp pico + sensor
\end{itemize}

\hypertarget{d-dual-sensor}{%
\subsection{1D: Dual Sensor}\label{d-dual-sensor}}

\begin{itemize}
\tightlist
\item
  gleicher abstand zwei gleicher sensoren
\item
  schnelle erkennung der plarisationsebene ggf offset vom mittelpunkt
  dieser
\end{itemize}

\hypertarget{full-sphere}{%
\subsection{Full-Sphere}\label{full-sphere}}

\begin{itemize}
\tightlist
\item
  komplexester aufbau sensor + mechanik
\item
  polar mechanisches system
\item
  full sphere sensor
\end{itemize}

\hypertarget{integration-of-an-professional-teslameter}{%
\subsection{Integration of an Professional
Teslameter}\label{integration-of-an-professional-teslameter}}

\begin{itemize}
\tightlist
\item
  einfach anbindung professioneller teslameter
\item
  Voltkraft
\end{itemize}

\hypertarget{software-readout-framework}{%
\chapter{Software readout framework}\label{software-readout-framework}}

\begin{figure}
\centering
\includegraphics{./generated_images/border_MRPlib_COMPLETE_FLOW.png}
\caption{MRPlib COMPLETE FLOW \label{MRPlib_COMPLETE_FLOW.png}}
\end{figure}

\hypertarget{library-requirements}{%
\section{Library requirements}\label{library-requirements}}

@@

\begin{itemize}
\tightlist
\item
  beispiele für projekte welche nur einzelne schnritte implementieren
\item
  so kann man sich auf die implementierung
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  grafik zeigen
\item
  einzelne module erleutern
\end{itemize}

\hypertarget{hal}{%
\subsubsection{HAL}\label{hal}}

\begin{itemize}
\tightlist
\item
  aufbau hal im grunde wird nur ein die commandos an das sensor cli
  weitergegeben
\item
  alle sensoren implementieren mehr oder weniger die gleichen befehle
\item
  hal gibt nur weiter und ist ``dumm''
\end{itemize}

\hypertarget{visualisation}{%
\subsubsection{Visualisation}\label{visualisation}}

\hypertarget{export}{%
\subsection{Export}\label{export}}

\begin{itemize}
\tightlist
\item
  format import export
\item
  matlab
\end{itemize}

\hypertarget{meta-data}{%
\subsubsection{Meta-Data}\label{meta-data}}

\hypertarget{multi-sensor-setup}{%
\subsection{Multi-Sensor setup}\label{multi-sensor-setup}}

At the moment, it is only possible to detect and use sensors that are
directly connected to the PC with the library. This has the disadvantage
that there must always be a physical connection. This can make it
difficult to install multiple sensors in measurement setups where space
or cable routing options are limited. To make sensors connected to a
small remote PC available on the network, the `Proxy' module has been
developed. This can be a single board computer (e.g.~a Raspberry Pi).
The small footprint and low power consumption make it a good choice. It
can also be used in a temperature chamber. The approach of implementing
this via a REST interface also offers the advantage that several
measurements or experiments can be recorded at the same time with the
sensors.

\begin{figure}
\centering
\includegraphics{./generated_images/border_MRPlib_Proxy_Module.png}
\caption{MRPlib Proxy Module \label{MRPlib_Proxy_Module.png}}
\end{figure}

Another application example is when sensors are physically separated or
there are long distances between them. By connecting several sensors via
the proxy module, it is possible to link several instances and all
sensors available in the network are available to the control PC.

\begin{figure}
\centering
\includegraphics{./generated_images/border_mrp_proxy_multi.png}
\caption{mrp proxy multi \label{mrp_proxy_multi.png}}
\end{figure}

The graphic \ref{mrp_proxy_multi.png} shows the modified multi-proxy -
multi-sensor topology. Here, both proxy instances do not communicate
directly with the control PC, but remote PC \#2 is connected to remote
PC \#1. This is then visible as a sensor opposite the Control PC, even
if there are several proxy instances behind it.

\hypertarget{network-proxy}{%
\subsubsection{Network-Proxy}\label{network-proxy}}

The graphic \ref{MRPlib_Proxy_Module.png} shows the separation of the
various HAL instances, which communicate with the physically connected
sensors on the remote PC and the control PC side, which communicates
with the remote side via the network. For the user, nothing changes in
the procedure for setting up a measurement. The proxy application must
always be started on the remote PC side.

\begin{lstlisting}[language=bash]
    # START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
    $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B # add another proxy instance http://proxyinstance_2.local for multi-sensor, multi-proxy chain
    Proxy started. http://0.0.0.0:5556/
    PRECHECK: SENSOR_HAL: 1337 # SENSOR A FOUND
    PRECHECK: SENSOR_HAL: 4242 # SENSOR B FOUND
    Terminate  [Y/n] [y]: 
\end{lstlisting}

After the proxy instance has been successfully started, it is optionally
possible to check the status via the REST interface:

\begin{lstlisting}[language=bash]
    # GET PROXY STATUS
    $ wget http://proxyinstance.local:5556/proxy/status
    {
    "capabilities":[
      "static",
      "axis_b",
      "axis_x",
      "axis_y",
      "axis_z",
      "axis_temp",
      "axis_stimestamp"
   ],
   "commands":[
      "status",
      "initialize",
      "disconnect",
      "combinedsensorcnt",
      "sensorcnt",
      "readsensor",
      "temp"
   ]
   # RUN A SENSOR COMMAND AND GET THE TOTAL SENSOR COUNT
   $ wget http://proxyinstance.local:5556/proxy/command?cmd=combinedsensorcnt
   {
   "output":[
      "2"
   ]
}
}
\end{lstlisting}

The query result shows that the sensors are connected correctly and that
their capabilites have also been recognised correctly. To be able to
configure a measurement on the other, only the IP address or host name
of the remote PC is required:

\begin{lstlisting}[language=bash]
    # START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
    $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B
    Proxy started. http://0.0.0.0:5556/
    PRECHECK: SENSOR_HAL: 1337 # SENSOR A FOUND
    PRECHECK: SENSOR_HAL: 4242 # SENSOR B FOUND
    Terminate  [Y/n] [y]: 
\end{lstlisting}

\hypertarget{sensor-syncronisation}{%
\subsubsection{Sensor Syncronisation}\label{sensor-syncronisation}}

\begin{itemize}
\tightlist
\item
  alle clients über ptp verbunden
\item
  zentraler reset zwischen zwei pps pulsen um den readout counter auf 0
  zu setzten
\end{itemize}

\hypertarget{command-router}{%
\subsubsection{Command-Router}\label{command-router}}

\begin{itemize}
\tightlist
\item
  nummerieierung zuerst lokale sensoren dann weitere proxy sensoren
\item
  commando templating
\end{itemize}

@@

@@

\begin{itemize}
\tightlist
\item
  automatische sensor dedettion
\item
  planung verschiedener messungen mit untersch. hardware
\item
  zentrale abarbeitung
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  datenanalyse für nicht programmieruer
\item
  automatisierter aufbau der call-tree
\item
  mit typcheck
\item
  alle funktionen mit bestimmer signtur werden automatisch aus globals
  geladen und stehen nutzer zur verfühung
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  drag\& drop system
\item
  automatische convertierung zum yaml system
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  verteilung durch paketmanager
\item
  docker cli beispiel
\end{itemize}

@@

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_testmagnets_in_holder.png}
\caption{testmagnets in holder \label{testmagnets_in_holder.png}}
\end{figure}

@@

\begin{itemize}
\tightlist
\item
  magfield camera
\end{itemize}
